\title{Geometrically Nonlinear Bending and Buckling Analysis of Shallow Spherical Shells}
\author{} \institute{}
\tocauthor{\underline{M.~Altekin}, R.~F.~Yukseler}
\maketitle

\begin{center}
{\large \underline{M. Altekin}, R. F. Yukseler}\\
Department of Civil Engineering, Yildiz Technical University\\
{\tt altekin@yildiz.edu.tr, yukseler@yildiz.edu.tr}
\end{center}

\section*{Abstract}
Geometrically nonlinear analysis of shallow spherical shells under uniform external pressure is made. Ordinary differential nonlinear shell equations are solved numerically by the finite difference and the Newton-Raphson methods. Totally six unkowns (three displacements and three stress resultants) are considered at each point along the radial coordinate. The study includes two cases: (i) the bending analysis is made by computing the displacements and stress resultants for uniform pressure, and (ii) the deflection-load curve is traced and the value of the external load corresponding to the first extremum of this curve is regarded as the critical (buckling) load. The material is assumed to be isotropic and homogeneous. The influence of the parameter of depth on the deflection and the critical load is investigated. The results obtained in the current work are compared with those available in the open literature.

\bibliographystyle{plain}
\begin{thebibliography}{10}
\bibitem{YamadaUchiyamaYamada83}
{\sc S.~Yamada, K.~Uchiyama, and  M.~Yamada}. {Experimental investigation of the buckling of shallow spherical shells}. Int. J. of Nonlinear  Mechanics 18  (1983), pp.~37--54.

\bibitem{TengRotter89}
{\sc J.G.~Teng, and J.M.~Rotter}. {Elastic-plastic large deflection analysis of axisymmetric shells}. Computers and Structures 31 (1989), pp.~211--233.

\bibitem{Huang64}
{\sc N.C.~Huang}. {Unsymmetrical buckling of thin shallow spherical shells}. J. of Applied Mechanics. 1 (1964), pp.~447--457.

\bibitem{Uddin87}
{\sc M.D.W. ~Uddin}. {Buckling of general spherical shells under external pressure}. Int. J. of Mechanical Sciences.  29 (1987), pp.~469--481.

\bibitem{Kai-YuanWei-PingCleghorn94}
{\sc Y.~Kai-Yuan, S.~Wei-Ping, and W.L.~Cleghorn}. {Axisymmetric buckling of thin shallow circular spherical shells under uniform pressure for large values of geometric parameter}. Int. J. of Nonlinear Mechanics 29 (1994), pp.~603--611.

\bibitem{NowinkaLukasiewicz91}
{\sc J.~Nowinka, and S.~Lukasiewicz}. {Symmetric elements in geometrical analysis of large deformations of spherical shells}. Int. J. of Nonlinear Mechanics. 26 (1991), pp.~151--168.
\end{thebibliography}