

% *****************************
% *   YOUR TEXT STARTS HERE   *
% *****************************

\title{Uintah - an Adaptive Scalable Framework for Fluid Structure Interaction.}
\author{} \institute{} % Intentionally left blank
\tocauthor{\underline{Martin Berzins},{Justin Luitjens}{Qingyu Meng}{Todd Harman}{Charles A. Wight}{Joseph R. Peterson} }
\maketitle
\begin{center}
\vspace{-4mm} % Use this space when including 3rd author
{\underline {Martin Berzins}, {Justin Luitjens}, {Qingyu Meng}}\\
SCI Institute, University of Utah, Salt Lake City UT 84112\\
{\tt mb@cs.utah.edu, luitjens@cs.utah.edu,  qymeng@cs.utah.edu}
%\vspace{4mm} % Use this space when including 3rd author
%{\large \underline{Justin Luitjens}}}\\
%SCI Institute, University of Utah, Salt Lake City UT 84112\\
%{\tt luitjens@cs.utah.edu}
%\vspace{4mm} % Use this space when including 3rd author
%{\large \underline{Qingyu Meng}}}\\
%SCI Institute, University of Utah, Salt Lake City UT 84112\\
%{\tt qymeng@cs.utah.edu}

%\vspace{-4mm} % Use this space when including 3rd author
{\large {Todd Harman}}\\
Department of Mechanical Engineering, University of Utah, Salt Lake City UT 84112\\
{\tt T.Harman@utah.edu}

%\vspace{-4mm} % Use this space when including 3rd author
{\large { Charles A. Wight, Joseph R. Peterson}}\\
Department of Chemistry, University of Utah, Salt Lake City UT 84112\\
{\tt Chuck.Wight@utah.edu, Joseph.R.Peterson@utah.edu}
\vspace{-4mm} % Use this space when including 3rd author
%{\large \underline{Joseph R. Peterson}}}\\
%Department of Chemistry, University of Utah, Salt Lake City UT 84112\\
%{\tt Joseph.R.Peterson@utah.edu}
\end{center}

\section*{Abstract}
%
%Enter your abstract here. Authors of contributed lectures: Please do not 
%exceed one page including references. References to related or 
%competitive work are mandatory. Presenting author should be underlined. 
%Please do not alter the internal structure of the template. Do not 
%introduce any new definitions or commands, they cause problems during the 
%compilation of the final Book of Abstract. The Book of Abstracts will be 
%compiled using pdflatex. If using images, please make sure thay are
%in PDF or PNG. Thank you!

The Uintah Software has been developed over the last decade 
\cite{csafe2,csafe3} to 
solve fluid-structure interaction problems on structured
adaptive grids on large-scale, long-running, data-intensive
problems, \cite{fourthmit}. Uintah uses flow solvers linked to
a particle method utlizing a finite element type formulation.
The challenge of making Uintah scale to large numbers of cores
on realistic engineering applications is addressed in this presentation.
Uintah uses a particularly simple block-structured AMR method, \cite{IPDPS10}. The scalability
of this method is contrasted with the Berger-Rigoutsos approach \cite{BergerRigoutsos}. 
Uintah uses a novel asynchronous task-based approach with
fully automated load balancing. This involves out of order execution of tasks \cite{Meng}  and measurement-based
load balancing. The application of Uintah to a petascale problem
in hazard analysis arising from {\it sympathetic} explosions in which the
collective interactions of a large ensemble of explosives results in
dramatically increased explosion violence, is considered, \cite{Ber2010b}. 
The advances in scalability and combustion
modeling needed to begin to solve this problem are discussed and illustrated by prototypical
computational results. Finally the challenges of multicore
architectures, are considered as is the potential for  
high-order methods (e.g. Discontinuous Galerkin) to compute solutions with the least 
energy use per significant digit of accuracy. 

\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{BergerRigoutsos}
M.~Berger and I.~Rigoutsos.
\newblock An algorithm for point clustering and grid generation.
\newblock {\em IEEE Trans. Systems Man Cybernet.}, 21(5):1278--1286, 1991.

\bibitem{Ber2010b}
M.~Berzins, J.~Luitjens, Q.~Meng, T.~Harman, C.~Wight, and J.~Peterson.
\newblock Uintah - a scalable framework for hazard analysis.
\newblock In {\em Proceedings of the Teragrid 2010 Conference}, number~3, page
  (published online), 2010.

\bibitem{csafe2}
J.~D. de~St.~Germain, J.~McCorquodale, S.~G. Parker, and C.~R. Johnson.
\newblock {U}intah: {A} massively parallel problem solving environment.
\newblock In {\em Ninth {IEEE} International Symposium on High Performance and
  Distributed Computing}, pages 33--41. {IEEE}, Piscataway, NJ, November 2000.

\bibitem{fourthmit}
J.~E. Guilkey, T.~B. Harman, and B.~Banerjee.
\newblock An eulerian-lagrangian approach for simulating explosions of
  energetic devices.
\newblock {\em Computers and Structures}, 85:660--674, 2007.
 
\bibitem{IPDPS10}
J.~Luitjens and M.~Berzins.
\newblock Improving the performance of {U}intah: {A} large-scale adaptive
  meshing computational framework.
\newblock In {\em Proceedings of the 24th IEEE International Parallel and
  Distributed Processing Symposium (IPDPS10)}, 2010. 

\bibitem{Meng}
Q. Meng, J. Luitjens, M. Berzins. 
\newblock Dynamic Task Scheduling for the Uintah Framework, 
\newblock In {\em Proceedings of the 3rd IEEE Workshop on Many-Task Computing on Grids and Supercomputers (MTAGS10)}, 2010.

\bibitem{csafe3}
S.~G. Parker, J.~Guilkey, and T.~Harman.
\newblock A component-based parallel infrastructure for the simulation of
  fluid-structure interaction.
\newblock {\em Engineering with Computers}, 22:277--292, 2006.

\end{thebibliography}

% ***************************
% *   YOUR TEXT ENDS HERE   *
% ***************************
