\title{Analysis of Earthquake Response of A Face Rock-fill Dam}
\author{Li Chenliang, Shen Zhenzhong, Jiao Ying} \institute{1.State Key Laboratory of Hydrology-Water Resources and Hydraulic Engineering.2.Institude of Hydraulic Structures,Hohai University, Nanjing 210098, P. R. China}

\begin{center}

\textbf{\Large Analysis of Earthquake Response of A Face Rock-fill Dam}\\
\vspace{10mm}
{\large Li Chenliang, Shen Zhenzhong}\\
Institude of Hydraulic Structures,Hohai University\\
{\tt chenliang-li@163.com, shen6627@yahoo.com.cn}

\end{center}

\section*{Abstract}

By use of the 3-dimensional dynamic non-linear FEM, the earthquake response behavior of Xigu Face Rock-fill Dam is researched in detail. The dynamic response properties of the dam are obtained at design peak acceleration of input earthquake curve, such as acceleration response, displacement response, stress response of dam body and concrete face, and displacement response of its peripheral joint and slab joint. Under an earthquake action with ten percent of exceeding probability in 50 years, the maximum acceleration reaction, displacement reaction and shear stress reaction of the dam body are 7.37m/s2, 81mm and 484kPa. The displacement response of peripheral joint and slab joint is very little. Calculation results show that the seismic stability of the dam body meets the specifications, and the design of the dam body is technically reasonable.

\bibliographystyle{plain}
\begin{thebibliography}{09}

\bibitem{XYZZSX 04}
{\sc Wen XY, Shen ZZ,and Lv SX}. {Study on Stress and Deformation Properties of Jiudianxia Concrete Face Rockfill Dam}. Journal of Hehai University (Natural Sciences ). 33(2005), pp.~42--46.

\bibitem{YZGC 04}
{\sc Dai YZ and Gu GC}. {Three-dimensional Nonlinear Analysis for Gongbo Gorge Concrete Face Rockfill Dam on the Yellow River}. Hongshui River. 20(2001), pp.~37--41.

\bibitem{GC 04}
{\sc Gu GC}. {Earthquake Engineering of Earth-Rock Fill Dams}.Hohai University Press (in Chinese). (1989).

\bibitem{SCGC 04}
{\sc Chi SC and Gu GC}. {Seismic stability Analysis of Concrete Face Rockfill Dam}. WATER RESOURSE HYDROPOWER OF NORTHEAST CHINA. 137(1995), pp.~3--5.

\bibitem{ZZMSX 04}
{\sc Shen ZZ, Ma M, and Lv SX}. {Seismic stability Analysis of Jiudianxia Concrete Face Rockfill Dam}. Conference Proceedings of First National Meeting on Hydraulic Earthquake and Disaster Prevention in China. (2006), pp.~273--278.

\bibitem{YZGC 04}
{\sc Dai YZ and  Gu GC}. {Three-dimensional Nonlinear Analysis for Gongbo Gorge Concrete Face Rockfill Dam on the Yellow River}. Hongshui River. 20(2001), pp.~37--41.

\bibitem{ZYZJ 04}
{\sc Xu ZY and Shen ZJ}. {Static and Dynamic Nonlinear Analysis and Seismic stability of High Tailing Dams}. Journal of East China Institute of Water Conservancy. 04(1980), pp.~1--17.

\bibitem{SSQYM 04}
{\sc Zhu S, Wen SQ,and Huang YM}. {Deformation and StressCalculation for A 200m High CFRD}. ournal of Hehai University (Natural Sciences ). 31(2003), pp.~631--634.

\bibitem{JMWS 04}
{\sc Zhao JM and Wang WS}. {Deformation and StressCalculation for A 200m High CFRD}. ournal of Hehai University (Natural Sciences ). 20(2001).

\end{thebibliography}