\title{Progress on High-Order Finite-Volume Methods}
\author{} \institute{}
\tocauthor{P. Colella}
\maketitle

\begin{center}
{\large Phillip Colella}\\
Computational Research Division, Lawrence Berkeley National Laboratory \\
{\tt PColella@lbl.gov}
\end{center}

\section*{Abstract}
In this talk, we will discuss recent progress in the design of higher-order (accuracy greater than second-order) finite-volume methods for conservation laws, i.e.  methods based on computing the divergence of a flux exactly, then introducing approximations in the quadrature rules for computing the averages of fluxes over cell faces. Topics to be discussed include: higher-order quadrature methods for computing flux integrals, and the application to time-dependent problems by using method of lines; methods for hyperbolic conservation laws using explicit Runge-Kutta methods, including high-order preserving limiters and adaptive mesh refinement; extension to semi-implicit methods for advection-diffusion problems and incompressible flow; and the extension to mapped and mapped-multiblock methods. We will show the use of these methods using examples from fluid dynamics and plasma physics.

\bibliographystyle{plain}
\begin{thebibliography}{10}
\bibitem{colella1}
\textsc{P. McCorquodale and P. Colella}. {A high-order finite-volume method for conservation laws on locally refined grids}. Communications in Applied Mathematics and Computational Science, Vol. 6 (2011), No. 1, 1-25.

\bibitem{colella2}
\textsc{P. Colella, M. R. Dorr, J. A. F. Hittinger and D.F. Martin}. {High-Order Finite-Volume Methods in Mapped Coordinates}. Journal of Computational Physics, 230(8):2952-2976 (2011).

\bibitem{colella3}
\textsc{Q. Zhang, H. Johansen and P. Colella}. {A Fourth-order Accurate Finite-volume Method with Structured Adaptive Mesh Refinement for Solving the Advection-Diffusion Equation}. SIAM J. Sci. Computing.

\bibitem{colella4}
\textsc{R. K. Crockett, P. Colella and D.T. Graves}. {A Cartesian grid embedded boundary method for solving the Poisson and heat equations with discontinuous coefficients in three dimensions}. Journal of Computational Physics.

\bibitem{colella5}
\textsc{E. Ateljevich, P. Colella, D. T. Graves, T. J. Ligocki, J. Percelay, P. O. Schwartz and Q. Shu}. {CFD Modeling in the San Francisco Bay and Delta}. 2009 Proceedings of the Fourth SIAM Conference on Mathematics for Industry (MI09), pp. 99-107 (2010).

\bibitem{colella6}
\textsc{C. Gatti-Bono, P. Colella and D. Trebotich}. {A Second-Order Accurate Conservative Front-Tracking Method in One Dimension}. SIAM J. Sci. Comput., 31(6):4795-4813 (2010).

\bibitem{colella7}
\textsc{P. Schwartz and P. Colella}. {A Second-Order Accurate Method for Solving the Signed Distance Function Equation}. Communications in Applied Mathematics and Computational Science, Vol. 5 (2010), No. 1, 81-97.
\end{thebibliography}