\title{Monolithic Model of Combined Electromagnetic-Thermoelastic Actuator for Accurate Setting of Position}
\author{} \institute{}
\tocauthor{\underline{I.~Dole\v{z}el}, V.~Kotlan, B.~Ulrych}
\maketitle

\begin{center}
{\large \underline{Ivo Dole\v{z}el}}\\
Institute of Thermomechanics, v.v.i., Academy of Sciences of the Czech Republic\\
{\tt dolezel@it.cas.cz}
\vspace{4mm}\\

{\large V\'{a}clav Kotlan, Bohu\v{s} Ulrych}\\
University of West Bohemia in Pilsen, Faculty of Electrical Engineering, RICE\\
{\tt vkotlan@kte.zcu.cz, ulrych@kte.zcu.cz}\\
\end{center}

\section*{Abstract}
An actuator for accurate setting of position based on a combined electromagnetic-thermoelastic principle is proposed and modeled. The device can be used in many technical domains such as optics, laser or microscope technologies, and others.

The device (with an axisymmetric arrangement) works in two steps. The first one is electromagnetic and its purpose is to set a rougher position. Its fine tuning is then realized thermoelastically in the following step. From the physical viewpoint, the device represents a strongly nonlinear system and modeling of both mentioned regimes represents a nonlinear and nonstationary coupled problem characterized by the interaction of electromagnetic field, temperature field and field of thermoelastic displacements. The authors modeled them numerically in the weakly coupled formulation in \cite{dolezel1} and \cite{dolezel2} for smaller
temperature variations of the active parts of the actuator. This paper presents their monolithic solutions using own codes Hermes2D and Agros2D \cite{dolezel3} based on a fully adaptive finite element method of higher order of accuracy and other algorithms described in \cite{dolezel4}. The results are evaluated and discussed.

This work was supported by the European Regional Development Fund and Ministry of Education, Youth and Sports of the Czech Republic under the project No. CZ.1.05/2.1.00/03.0094: Regional Innovation Center for Electrical Engineering (RICE), further by Grant project GACR 102/09/1305 and Research Plan MSM6840770017.

\bibliographystyle{plain}
\begin{thebibliography}{10}
\bibitem{dolezel1}
{\sc I.~Dole\v{z}el, B. Ulrych, and V. Kotlan}. {Combined electromagnetic-thermoelastic actuator for accurate setting of position}. Proc. EPNC 2010 Essen, Germany, pp.~53--54.

\bibitem{dolezel2}
{\sc I.~Dole\v{z}el, V. Kotlan, and B. Ulrych}. {Electromagnetic-thermoelastic actuator for accurate wide-range setting of position}. Przegl\c{a}d Elektrotechniczny (Electrical Review) 87/04 (2011), accepted.

\bibitem{dolezel3}
{http://hpfem.org}.

\bibitem{dolezel4}
{\sc P.~Solin, J.~Cerveny, L.~Dubcova, and D.~Andrs}. {Monolithic discretization of linear thermoelasticity problems via adaptive multimesh \textit{hp}-FEM}. J. Comput. Appl. Math. 234 (2010), pp.~2350--2357.
\end{thebibliography}