\title{Development of a Reactor System Analysis Code using TRILINOS}
\author{} \institute{}
\tocauthor{\underline{G.~Hansen}, V.~Mousseau}
\maketitle

\begin{center}
{\large \underline{Glen Hansen}, Vincent Mousseau}\\
Idaho National Laboratory\\
{\tt Glen.Hansen@inl.gov, Vincent.Mousseau@inl.gov}
\end{center}

\section*{Abstract}
This presentation gives an overview of the development of RELAP6, a reactor thermal-hydraulics code that is based on the TRILINOS multiphysics framework from Sandia National Laboratories (\url{http://trilinos.sandia.gov}). The software constructs a dynamic rendition of the reactor facility geometry using models from component libraries and input files. The components interconnect to form a simple graph, where each component supports the required degrees of freedom (DOF) needed to support the spatial resolution needed for the analysis of the component's thermal-hydraulic behavior. The component DOF are assembled together with an ordering determined by the connectivity of the graph to form a vector of nonlinear algebraic equations.  The component graph can construct an initial condition vector given the initial state of the components, or can create a residual vector that is valid for any time state of the system. These initial conditions and system residual is used by TRILINOS' NOX nonlinear solver, various linear solvers and preconditioner packages, to obtain the state of the system each time step. Typically, this provides an implicit Jacobian-free Newton Krylov solution method that provides for stable, parallel system simulation given the user's choice of time step.

The software system leverages the CMAKE build system within TRILINOS and the CTEST testing system for regression testing. Details of the software architecture, capabilities, and design strategy will be discussed in detail.

\bibliographystyle{plain}
\begin{thebibliography}{1}
\bibitem{gaston09a}
\textsc{D.~Gaston, G.~Hansen, S.~Kadioglu, D.~Knoll, C.~Newman, H.~Park, C.~Permann, and W.~Taitano}.
\newblock Parallel multiphysics algorithms and software for computational nuclear engineering.
\newblock {\em Journal of Physics: Conference Series}, 180(1):012012, 2009.

\bibitem{pope:09}
\textsc{M.~A. Pope and V.~A. Mousseau}.
\newblock Accuracy and efficiency of a coupled neutronics and thermal hydraulics model.
\newblock {\em Nuclear Engineering and Technology}, 41(7):885--892, 2009.
\end{thebibliography}