\title{GPU Experiences for Applications in Computational Mechanics}
\author{} \institute{}
\tocauthor{\underline{S.~Kodiyalam}, S.~Posey}
\maketitle

\begin{center}
{\large \underline{Srinivas Kodiyalam}, Stan Posey}\\
NVIDIA, Santa Clara CA\\
{\tt skodiyalam@nvidia.com, sposey@nvidia.com}
\end{center}

\section*{Abstract}
Current trends in high performance computing (HPC) are moving towards the availability of several cores on the same chip of contemporary processors in order to achieve speed-up through the extraction of potential fine-grain parallelism of applications. The trend is led by GPUs, which have been developed exclusively for computational tasks as massively-parallel co-processors to the CPU. During 2010 an extensive set of new HPC architectural feature were developed in the third generation of NVIDIA GPUs (Fermi), giving computational mechanics an opportunity to expand use of GPU modelling and simulation.

This presentation will examine examples relevant to industry-scale HPC practice of GPU-accelerated computational structural mechanics and computational fluid dynamics software that support product design in manufacturing industries. For each example, the choice of CPU-GPU system configurations will be described based upon the physics features, and resolution requirements of a particular simulation. Performance results compare use of conventional CPUs with and without GPU acceleration.

\bibliographystyle{plain}
\begin{thebibliography}{10}
\bibitem{kodiyalam1}
\textsc{R. Lucas, G. Wagenbreth, D. Davis}. {Implementing a GPU-Enhanced Cluster for Large Scale Simulations}. I/ITSEC, 2007. Orlando, FL.  

\bibitem{kodiyalam2}
\textsc{S. Kodiyalam, M. Kremenetsky, S. Posey}. {Balanced HPC Infrastructure for CFD and Associated Multidiscipline Simulations of Engineering Systems}. 7th Asia CFD Conference 2007. Bangalore, India, November 26 – 30, 2007.

\bibitem{kodiyalam3}
\textsc{A. Corrigan, F. Camelli, R. Lohner, Mut, F.}. {Porting of an edge-based CFD solver to GPUs}. 48th AIAA Aerospace Sciences Meeting Including The New Horizons Forum and Aerospace Exposition, number AIAA-2010-522. Orlando, FL, January 2010.

\bibitem{kodiyalam4}
\textsc{P. LeGresley, E. Elsen, E. Darve}. {Large calculation of the flow over a hypersonic vehicle using a GPU}. Journal of Computational Physics, 227:10148-10161. 2008.

\bibitem{kodiyalam5}
\textsc{N. Bell, M. Garland}. {Implementing sparse matrix-vector multiplication on throughput-oriented processors}. SC '09: Proceedings of the Conference on High Performance Computing Networking, Storage and Analysis, pages 1-11. New York, NY, USA, 2009. ACM.

\bibitem{kodiyalam6}
\textsc{T. Brandvik, G. Pullan}. {An accelerated 3D Navier-Stokes Solver for Flows in Turbomachines}. Proceedings of GT2009 ASME Turbo Expo 2009: Power for Land, Sea and Air, June 2009.

\bibitem{kodiyalam7}
\textsc{ACUSIM Corporation, AcuSolve}. www.acusim.com.
\end{thebibliography}