
% *****************************
% *   YOUR TEXT STARTS HERE   *
% *****************************

\title{
Acceleration of Uncertainty Updating in Description of Transport Processes
in Heterogeneous Materials}
\author{} \institute{} % Intentionally left blank
\tocauthor{\underline{Anna Ku\v{c}erov\'a}, Jan S\'ykora, Hermann G. Matthies}
\maketitle
\begin{center}
{\large \underline{Anna Ku\v{c}erov\'a}}\\
CTU in Prague, Faculty of Civil Eng., Dept. of Mechanics, Th\'akurova 7, Prague, Czech Republic\\
{\tt anicka@cml.fsv.cvut.cz}\\
\vspace{4mm} % Use this space when including 3rd author
{\large Jan S\'ykora}\\
CTU in Prague, Faculty of Civil Eng., Dept. of Mechanics, Th\'akurova 7, Prague, Czech Republic\\
{\tt jan.sykora.1@fsv.cvut.cz}\\
\vspace{4mm} % Use this space when including 3rd author
{\large Hermann G. Matthies}\\
TU Braunschweig, Inst. of Scientific Computing, Hans-Sommer-Str. 65, Braunschweig, Germany\\
{\tt wire@tu-bs.de}\\
\vspace{4mm} % Use this space when including 3rd author
{\large Bojana Rosi\'c}\\
TU Braunschweig, Inst. of Scientific Computing, Hans-Sommer-Str. 65, Braunschweig, Germany\\
{\tt bojana.rosic@tu-bs.de}
\end{center}

\section*{Abstract}

Structural durability is highly influenced by heat and moisture
transport. Proper estimation of the durability, therefore, needs a
reliable and probabilistic simulation of transport processes.  The
reliability a such simulation is related to the suitable
identification of material parameters. To include any expert knowledge
together with experimental results, one can employ an updating
procedure, which makes the identification very computationally
demanding.

Here, the novel stochastic computational techniques like generalized
polynomial chaos expansion (PCE) are used for much faster updating
procedure by replacing the computationally expensive forward
simulation via a FE-program by the PCE via a stochastic FE-computation
\cite{Matthies:2007:IB}. This inexpensive PCE-forward model can then
be used in the Bayesian updating \cite{Kucerova:2010:AMC}. 

The presented uncertainty updating techniques are applied to the
numerical model of coupled heat and moisture transport
\cite{Kunzel:1997} for heterogeneous material, where the particular
transport coefficients are not spatially constant and can be described
by correlated random fields.

\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{Kucerova:2010:AMC} 
{\sc A.~Ku\v{c}erov\'a and J.~S\'ykora}.
{Uncertainty Updating in the Description of Coupled Heat and
Moisture Transport in Heterogeneous Materials}. Appl. Math.
Comput. 0 (2010), pp.~0--0.

\bibitem{Kunzel:1997}
{\sc H.~M.~ K\"{u}nzel and K.~Kiessl}. {Calculation of heat and
moisture transfer in exposed building components}. Int. J. Heat Mass
Tran. 40 (1997), pp.~159--167.

\bibitem{Matthies:2007:IB}
{\sc H.~G.~Matthies}. {Encyclopedia of Computational Mechanics},
chapter Uncertainty Quantification with Stochastic Finite
Elements. John Wiley \& Sons, Ltd., 2007.

\end{thebibliography} 

% ***************************
% *   YOUR TEXT ENDS HERE   *
% ***************************
