
% *****************************
% *   YOUR TEXT STARTS HERE   *
% *****************************

\title{Improved Continuum Skin and Proximity Effect Model for Hexagonally Packed Wires }
\author{} \institute{} % Intentionally left blank
\tocauthor{David Meeker}
\maketitle
\begin{center}
{\large David Meeker}\\
QinetiQ North America\\
350 Second Avenue \\
Waltham, MA 02451 \\
{\tt dmeeker@ieee.org}\\
% \vspace{4mm} % Use this space when including 3rd author
%{\large \underline{Second Author}}\\
%Address of Second Author\\
%{\tt email@of.second.author}
\end{center}

\section*{Abstract}

This work develops accurate closed-form expressions for ``effective''
complex-valued magnetic permeability and electric conductivity that
represent the effects of proximity and hysteresis losses in wound coils.
These material properties can then be used in 2D/axisymmetric finite element
models in which the coil is modeled as a coarsely meshed, homogeneous region
({\em i.e.} removing the need for modeling each turn in the coil). The
practically useful case of circular wires in a hexagonal packed coil is
addressed.

A novel method for computing effective material properties via 2D finite
elements is presented. Effective material property results are tabulated
over a wide range of frequencies and packing factors using these methods. 
Closed-form expressions for approximating these results are then presented.
These closed-form expressions yield improved accuracy over previous
expressions based on an equivalent foil approach, especially at very high or
very low packing factors. Several examples demonstrate good agreement
between between total losses computed from a homogenized coil model with
those computed from a model in which each turn is individually modeled.

\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{Moreau} O. Moreau, L. Popiel, and J. L. Pages,``Proximity losses computation with
a 2D complex permeability modelling,'' \emph{IEEE Trans. Magn.}, vol. 34, pp. 3616-3619, Sept. 1998.

\bibitem{Gyselinck} J. Gyselinck and P. Dular, ``Frequency-domain
homogenization of bundles of wires in 2-D magnetodynamic FE
calculations,'' \emph{IEEE Trans. Magn.}, vol. 41, pp. 1416-1419,
May 2005.

\bibitem{Meeker}
D. C. Meeker,''Effective Material Properties of Wound Coils from an Equivalent Foil Approach'', {\tt
http://www.femm.info/examples/prox/notes.pdf}.



\end{thebibliography}

% ***************************
% *   YOUR TEXT ENDS HERE   *
% ***************************
