
%%%%% HEADING %%%%%

\vspace{5ex}

\begin{center}
%%%%% TITLE %%%%%
\textbf{\large
High-Order Discontinuous Galerkin Simulation of Flapping Wings
}

%%%%% AUTHORS %%%%%
\textbf{
Per-Olof Persson
}

%%%%% AFFILIATIONS %%%%%
Per-Olof Persson \\
Department of Mathematics, UC Berkeley \\
970 Evans Hall \#3840, Berkeley, CA 94720 \\
persson@berkeley.edu

\end{center}

The numerical simulation of flapping flight is a challenging
problem, partly because of the large deformations of the computational
domain, the transitional flows, and the complex geometries. We present
our recent results with high-order accurate discontinuous Galerkin
methods, which are capable of accurately solving complex flow problems
on unstructured meshes [1]. We generate tetrahedral meshes using the
DistMesh mesh generator and the Delaunay refinement method. The
elements are curved to align with the boundaries using a nonlinear
elasticity analogy [2].

The moving domain is modeled by a mapping-based high-order accurate
Arbitrary Lagrangian-Eulerian formulation [3]. We explore various
mappings, including explicitly prescribed expressions as well as
numerical ones. The equations are discretized using the Compact DG
method [4], and solved efficiently in parallel using Newton-Krylov
solvers and optimized element ordering [5]. We study several flapping
strategies and flow parameters, and determine in which regimes a
high-fidelity approach is required and when faster simulation tools
could be used [6].


%%%%% REFERENCES %%%%%
\textbf{References}

[1] A. Uranga, P.-O. Persson, M. Drela, and J. Peraire, ``Implicit
Large Eddy Simulation of transition to turbulence at low Reynolds
numbers using a Discontinuous Galerkin method,'' \emph{Int. J. Num.
  Meth. Engrg.}, to appear. \\ \vspace{-9mm}

[2] Persson, P.-O. and Peraire, J., ``Curved Mesh Generation and Mesh
Refinement using Lagrangian Solid Mechanics,'' \emph{47th AIAA
  Aerospace Sciences Meeting and Exhibit}, Orlando, Florida, 2009,
AIAA-2009-949. \\ \vspace{-9mm}

[3] Persson, P.-O., Bonet, J., and Peraire, J., ``Discontinuous
Galerkin Solution of the Navier-Stokes Equations on Deformable
Domains,'' \emph{Comput. Methods Appl. Mech. Engrg.}, Vol. 198, No.
17--20, 2009, pp. 1585--1595. \\ \vspace{-9mm}

[4] Peraire, J. and Persson, P.-O., ``The compact discontinuous
Galerkin (CDG) method for elliptic problems,'' \emph{SIAM J. Sci.
  Comput.}, Vol. 30, No. 4, 2008, pp. 1806--1824. \\ \vspace{-9mm}

[5] Persson, P.-O., ``Scalable Parallel Newton-Krylov Solvers for
Discontinuous Galerkin Discretizations,'' \emph{47th AIAA Aerospace
  Sciences Meeting and Exhibit}, Orlando, Florida, 2009,
AIAA-2009-606. \\ \vspace{-9mm}

[6] Persson, P.-O., Willis, D. J., and Peraire, J., ``The Numerical
Simulation of Flapping Wings at Low Reynolds Numbers,'' \emph{48th
  AIAA Aerospace Sciences Meeting and Exhibit}, Orlando, Florida,
January 2010, AIAA-2010-724.
