\title{Finite Element Network Analysis of Random Particle Composites}
\author{} \institute{}
\tocauthor{D.~Peterseim}
\maketitle

\begin{center}
{\large Daniel Peterseim}\\
Humboldt-Universit\"at zu Berlin\\
{\tt peterseim@math.hu-berlin.de}\\
\end{center}

\section*{Abstract}
The numerical simulation of partial differential equations is particularly challenging if the underlying data is complicated, e.g., if non-uniform, heterogeneous or oscillating diffusion coefficients are considered. 

In this respect, a new finite element method \cite{PeCa10}
is presented which computes conductivity in some unstructured particle-reinforced composite material and thereby covers applications in thermodynamics, mechanics, or electromagnetism. The $2$-phase material under consideration is composed of a poorly conducting matrix material filled by highly conducting circular inclusions which are randomly dispersed. The mathematical model is a Poisson-type problem with discontinuous coefficients. The discontinuities are huge in contrast and quantity.

The proposed method generalizes classical continuous piecewise affine finite elements to special computational meshes which encode the particles in a network structure \cite{DP09,P10}.
This approach preserves important quantities like volume and surface fractions exactly and mimics macroscopic phenomena such as a maximum principle and percolation phenomena. The discretization error is proportional to the particle distance and does not depend on the conductivity contrast in the medium.

This research aims at a better understanding of how macroscopic material properties depend on the microscopic geometry. A precise knowledge of such dependencies is of enormous importance since shape parameters of the filler particles are often at manufacturer's disposal and can be adjusted within material optimization.

\bibliographystyle{plain}
\begin{thebibliography}{10}
\bibitem{PS11}
\textsc{D.~Peterseim and S.~Sauter}.
\newblock Error Estimates for Finite Element Discretizations of Elliptic Problems with Oscillatory Coefficients.
\newblock {\em DFG Research Center Matheon Berlin, Preprint Series}, 756, 2011.
\newblock (submitted for publication)

\bibitem{PeCa10}
\textsc{D.~Peterseim and C.~Carstensen}.
\newblock Finite Element Network Approximation of Conductivity in Particle Composites.
\newblock 2010.
\newblock (submitted for publication)

\bibitem{DP09}
\textsc{D.~Peterseim}.
\newblock Generalized {D}elaunay Partitions and Composite Material Modeling.
\newblock {\em DFG Research Center Matheon Berlin, Preprint Series}, 690, 2010.
\newblock (submitted for publication)

\bibitem{P10}
\textsc{D.~Peterseim}.
\newblock Triangulating a System of Disks.
\newblock In {\em Proceedings of the EuroCG 2010, Dortmund, Germany}, 2010.
\end{thebibliography}