\title{Acceleration of Uncertainty Updating in Description of Transport Processes in Heterogeneous Materials}
\author{} \institute{}
\tocauthor{Anna Ku\v{c}erov\'a,\underline{Jan S\'ykora}, Hermann G. Matthies}

\begin{center}

\textbf{\Large Acceleration of Uncertainty Updating in Description of Transport Processes in Heterogeneous Materials}\\
\vspace{10mm}
{\large Anna Ku\v{c}erov\'a, \underline{Jan S\'ykora}}\\
CTU in Prague, Faculty of Civil Eng., Dept. of Mechanics, Th\'akurova 7, Prague, Czech Republic\\
{\tt anicka@cml.fsv.cvut.cz, jan.sykora.1@fsv.cvut.cz}\\
\vspace{4mm}
{\large Hermann G. Matthies, Bojana Rosi\'c}\\
TU Braunschweig, Inst. of Scientific Computing, Hans-Sommer-Str. 65, Braunschweig, Germany\\
{\tt wire@tu-bs.de, bojana.rosic@tu-bs.de}

\end{center}

\section*{Abstract}

Structural durability is highly influenced by heat and moisture transport. Proper estimation of the durability, therefore, needs a reliable and probabilistic simulation of transport processes.  The reliability of such simulation is related to the suitable identification of material parameters. To include some expert knowledge (e.g. positivity or realistic bounds of parameters) together with experimental results, one can employ an updating procedure, where prior distributions based on expert's recommendations are updated by measurements in order to obtain more reliable a posteriori distributions~\cite{Kucerova:2010:AMC}. This procedure usually involving Monte Carlo sampling is however very computationally demanding.

Here, the novel stochastic computational techniques like generalized polynomial chaos expansion (PCE) are used for much faster updating procedure by replacing the computationally expensive forward simulation via a FE-program by the PCE via a stochastic FE-computation \cite{Matthies:2007:IB}. This inexpensive PCE-forward model can then be used in the Bayesian updating as in the \cite{Kucerova:2010:AMC}.

The presented uncertainty updating techniques are applied to the numerical model of coupled heat and moisture transport \cite{Kunzel:1997} for heterogeneous material, where the particular transport coefficients are not spatially constant and can be described by correlated random fields.

\bibliographystyle{plain}
\begin{thebibliography}{10}

\bibitem{Kucerova:2010:AMC}
{\sc A.~Ku\v{c}erov\'a and J.~S\'ykora}.
{Uncertainty Updating in the Description of Coupled Heat and Moisture Transport in Heterogeneous Materials}. Appl. Math. Comput. (2011) Accepted for publication.

\bibitem{Kunzel:1997}
{\sc H.~M.~ K\"{u}nzel and K.~Kiessl}. {Calculation of heat and moisture transfer in exposed building components}. Int. J. Heat Mass Tran. 40 (1997), pp.~159--167.

\bibitem{Matthies:2007:IB}
{\sc H.~G.~Matthies}. {Encyclopedia of Computational Mechanics}, chapter Uncertainty Quantification with Stochastic Finite Elements. John Wiley \& Sons, Ltd., 2007.

\end{thebibliography}