\title{Acceleration of Uncertainty Updating in Description of Transport Processes in Heterogeneous Materials}
\author{} \institute{}
\tocauthor{A.~Ku\v{c}erov\'a, \underline{J.~S\'ykora}, H.~G.~Matthies, B.~Rosi\'c}
\maketitle

\begin{center}
{\large Anna Ku\v{c}erov\'a, \underline{Jan S\'ykora}}\\
Department of Mechanics, Faculty of Civil Engneering, CTU in Prague\\
{\tt anicka@cml.fsv.cvut.cz, jan.sykora.1@fsv.cvut.cz}\\
\vspace{4mm}

{\large Hermann G. Matthies, Bojana Rosi\'c}\\
TU Braunschweig, Inst. of Scientific Computing\\
{\tt wire@tu-bs.de, bojana.rosic@tu-bs.de}
\end{center}

\section*{Abstract}
Structural durability is highly influenced by heat and moisture transport. Proper estimation of the durability, therefore, needs a reliable and probabilistic simulation of transport processes.  The reliability a such simulation is related to the suitable identification of material parameters. To include any expert knowledge together with experimental results, one can employ an updating procedure, which makes the identification very computationally demanding.

Here, the novel stochastic computational techniques like generalized polynomial chaos expansion (PCE) are used for much faster updating procedure by replacing the computationally expensive forward simulation via a FE-program by the PCE via a stochastic FE-computation \cite{Matthies:2007:IB}. This inexpensive PCE-forward model can then be used in the Bayesian updating \cite{Kucerova:2010:AMC}.

The presented uncertainty updating techniques are applied to the numerical model of coupled heat and moisture transport \cite{Kunzel:1997} for heterogeneous material, where the particular transport coefficients are not spatially constant and can be described by correlated random fields.

\bibliographystyle{plain}
\begin{thebibliography}{10}
\bibitem{Kucerova:2010:AMC} 
{\sc A.~Ku\v{c}erov\'a and J.~S\'ykora}. {Uncertainty Updating in the Description of Coupled Heat and Moisture Transport in Heterogeneous Materials}. Appl. Math. Comput. 0 (2010), pp.~0--0.

\bibitem{Kunzel:1997}
{\sc H.~M.~ K\"{u}nzel and K.~Kiessl}. {Calculation of heat and moisture transfer in exposed building components}. Int. J. Heat Mass Tran. 40 (1997), pp.~159--167.

\bibitem{Matthies:2007:IB}
{\sc H.~G.~Matthies}. {Encyclopedia of Computational Mechanics}, chapter Uncertainty Quantification with Stochastic Finite Elements. John Wiley \& Sons, Ltd., 2007.
\end{thebibliography}