\title{OFELI: An Object-Oriented Finite Element Library}
\author{} \institute{}
\tocauthor{Rachid Touzani}
\maketitle

\begin{center}
{\large Rachid Touzani}\\
Laboratoire de Math\'ematiques, UMR CNRS\\
Universit\'e Blaise Pascal (Clermont-Ferrand 2)\\
{\tt rachid.touzani@univ-bpclermont.fr}
\end{center}

\section*{Abstract}
We present, in this contribution the library OFELI  (Object Finite Element Library). OFELI is a multipurpose finite element library written in C++. OFELI is designed as an efficient tool for constructing large size finite element codes for coupled problems in 2-D and 3-D. Classes for mesh handling, linear system solving, optimization, eigenvalue extraction, \ldots are provided to solve various types of problems and to deal with a large variety of numerical methods. We present some examples of developed codes in CFD, electromagnetics and solid mechanics and emphasize on some particular applications such as:
\begin{itemize}
\item A projection finite element code for time dependent incompressible Navier-Stokes equations (\cite{PhC}).
\item A finite element code for three-dimensional elasticity.
\item A mixed hybrid finite element method for the Laplace equation (see \cite{Djenno}).
\item A MUSCL finite volume solver for compressible Euler equations (see \cite{CC,CR}).
\item A numerical code for the simulation of inductively coupled plasma torches.
\end{itemize}
Other applications in chemistry like \cite{SSDTZ} can be mentioned in this context.

The library is provided with some prototype codes to illustrate its use. OFELI is free but copyrighted under the LGPL license.

\bibliographystyle{plain}
\begin{thebibliography}{10}
\bibitem{PhC}
{\sc P.~Caussignac}. {A gauge finite element method for the 2D Navier--Stokes problem}. Applied Numerical Mathematics, 58(10), doi: 1016/j.apnum.2007.08.002 (2007).

\bibitem{CC}
{\sc S. Clain and V. Clauzon}. {The multi-slopes MUSCL method}. Proceeding in the Finite Volumes for Complex Application 5, Wiley Editor (2008), pp.~297--304.

\bibitem{CR}
{\sc S.~Clain and D.~Rochette}. {First- and second-order finite volume methods for the one-dimensional nonconservative Euler system}. J. Comp. Phys., 28(22), doi: 10.1016/j.jcp.2009.07.038 (2009).

\bibitem{Djenno}
{\sc M. Djenno}. {Nouvelles approximations num\'eriques pour les \'equations de Stokes et l'\'equation Level Set}. PhD Thesis, Universit\'e Blaise Pascal, France (2007).

\bibitem{SSDTZ}
{\sc \L.~Sochaczewski, A.~Stockdale, W.~Davison, W.~Tych, and H.~Zhang}. {A three-dimensional reactive transport model for sediments, incorporating microniches}. Environmental Chemistry, 5(3), doi: 10.1071/EN08006 (2008),  pp.~218--225.
\end{thebibliography}